\propertitle

### 2019-12-26 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-22T15:09:24+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Inferences about large neuronal populations}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\texttt{\urlalt{https://arxiv.org/abs/#1}{arXiv:\hspace{0pt}#1}}%

@@

\texttt{\urlalt{http://www.ma.utexas.edu/mp_arc-bin/mpa?yn=#1}{mp\_arc:\hspace{0pt}#1}}%

@@

\texttt{\urlalt{https://hal.archives-ouvertes.fr/#1}{HAL:\hspace{0pt}#1}}%

@@

\texttt{\urlalt{http://philsci-archive.pitt.edu/archive/#1}{PhilSci:\hspace{0pt}#1}}%

@@

\texttt{\urlalt{https://doi.org/10.1101/#1}{bioRxiv doi:\hspace{0pt}10.1101/#1}}%

@@

\texttt{\urlalt{https://doi.org/10.17605/osf.io/#1}{Open Science Framework doi:10.17605/osf.io/#1}}%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abstractrunin
\abslabeldelim{}
\renewcommand*{\abstractname}{}
\setlength{\absleftindent}{0pt}
\setlength{\absrightindent}{0pt}
\setlength{\abstitleskip}{-\absparindent}
\begin{abstract}\labelsep 0pt%
\mynote{to be written}
% \noindent \mynote{Abstract must be rewritten once paper is ready}This
%   work shows how to build a maximum-entropy probabilistic model for the
%   total activity of a population of neurons, given only some activity data or
%   statistics -- for example, empirical moments -- of a \emph{subpopulation}
%   thereof. This kind of model is useful because neuronal recordings are
%   always limited to a very small sample of a population of neurons.
% %
%   The model is applied to two sets of neuronal data available in the
%   literature. In some cases it makes interesting forecasts about the larger
%   population -- for example, two low-regime modes in the frequency
%   distribution for the total activity -- that are not visible in the sample
%   data or in maximum-entropy models applied only to the sample.
% %
%   For the two datasets, the maximum-entropy probability model applied only
%   to the subpopulation is compared with the marginal probability
%   distribution obtained from the maximum-entropy model applied to the full
%   population. On a linear probability scale no large differences are
%   visible, but on a logarithmic scale the two distributions show very
%   different behaviours, especially in the tails.
  \\\noindent\emph{\footnotesize Note: Dear Reader \amp\ Peer, this
    manuscript is being peer-reviewed by you. Thank you.}
% \par%\\[\jot]
% \noindent
% {\footnotesize PACS: ***}\qquad%
% {\footnotesize MSC: ***}%
%\qquad{\footnotesize Keywords: ***}
\end{abstract}
\selectlanguage{british}\frenchspacing

@@

By \enquote{inference} we mean the quantification of a degree of belief
about possible observations, based on specific assumptions; not the
response of an oracle. The model here presented gives us a \emph{forecast}
based on specific assumptions discussed in \sect~\ref{sec:assumptions}, and
therefore has two main uses, just like any other probabilistic model. If
our assumptions are only hypotheses under testing, then the subsequent
confirmation or confutation of the forecast will increase or decrease our
confidence in those hypotheses. If we strongly trust our assumptions, on
the other hand, then we rely on the forecast and even use it in place of
actual observations, especially if the latter are difficult to make. (In
fact, we typically shift from the first to the second use.) In the
preceding sections we have given examples of additional hypotheses that
could be explored with the present model. The assumptions of the model
itself (\sect~\ref{sec:assumptions}) can either be under test or relied
upon, depending on the case.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-26T15:35:20+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Inferences about large neuronal populations}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\texttt{arXiv:\urlalt{https://arxiv.org/abs/#1}{#1}}%

@@

\texttt{mp\_arc:\urlalt{http://www.ma.utexas.edu/mp_arc-bin/mpa?yn=#1}{#1}}%

@@

\texttt{HAL:\urlalt{https://hal.archives-ouvertes.fr/#1}{#1}}%

@@

\texttt{PhilSci:\urlalt{http://philsci-archive.pitt.edu/archive/#1}{#1}}%

@@

\texttt{bioRxiv doi:\urlalt{https://doi.org/10.1101/#1}{10.1101/#1}}%

@@

\texttt{Open Science Framework doi:\urlalt{https://doi.org/10.17605/osf.io/#1}{10.17605/osf.io/#1}}%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abstractrunin
\abslabeldelim{}
\renewcommand*{\abstractname}{}
\setlength{\absleftindent}{0pt}
\setlength{\absrightindent}{0pt}
\setlength{\abstitleskip}{-\absparindent}
\begin{abstract}\labelsep 0pt%
\mynote{Abstract to be written}
% \noindent \mynote{Abstract must be rewritten once paper is ready}This
%   work shows how to build a maximum-entropy probabilistic model for the
%   total activity of a population of neurons, given only some activity data or
%   statistics -- for example, empirical moments -- of a \emph{subpopulation}
%   thereof. This kind of model is useful because neuronal recordings are
%   always limited to a very small sample of a population of neurons.
% %
%   The model is applied to two sets of neuronal data available in the
%   literature. In some cases it makes interesting forecasts about the larger
%   population -- for example, two low-regime modes in the frequency
%   distribution for the total activity -- that are not visible in the sample
%   data or in maximum-entropy models applied only to the sample.
% %
%   For the two datasets, the maximum-entropy probability model applied only
%   to the subpopulation is compared with the marginal probability
%   distribution obtained from the maximum-entropy model applied to the full
%   population. On a linear probability scale no large differences are
%   visible, but on a logarithmic scale the two distributions show very
%   different behaviours, especially in the tails.
  \\\noindent\emph{\footnotesize Note: Dear Reader \amp\ Peer, this
    manuscript is being peer-reviewed by you. Thank you.}
% \par%\\[\jot]
% \noindent
% {\footnotesize PACS: ***}\qquad%
% {\footnotesize MSC: ***}%
%\qquad{\footnotesize Keywords: ***}
\end{abstract}
\selectlanguage{british}\frenchspacing

@@

By \enquote{inference} we mean the quantification of a degree of belief
about possible observations, based on specific assumptions; not the
response of an oracle. The model here presented gives us a \emph{forecast}
based on specific assumptions discussed in \sect~\ref{sec:assumptions}, and
therefore has two main uses, just like any other probabilistic model. If
our assumptions are only hypotheses under testing, then the subsequent
confirmation or confutation of the forecast will increase or decrease our
confidence in those hypotheses. If we strongly trust our assumptions, on
the other hand, then we rely on the forecast and even use it in place of
actual observations, especially if the latter are difficult to make. (In
fact, we typically shift from the first to the second use.) In the
preceding sections we have given examples of additional hypotheses that
could be explored with the present model. The assumptions of the model
itself, discussed in \sect~\ref{sec:assumptions}, can either be under test
or relied upon, depending on the case.
